---
title: "FDA Analysis - Meta Analysis and Plots"
author: "Brooke Fridley"
date: "`r Sys.Date()`"
output: word_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(tidyverse)
library(ggplot2)
library(readxl)
library(knitr)
library(meta)
library(grid)


```

# Background and Methods

* Meta-Analysis of results from Functional Data Analysis (FDA) using K and G for a range of radii.

* Each cohort analyzed individually.Meta-analysis was a random effect meta-analysis based on inverese-variance approach. Test Statistic was the log(HR) and the SE(logHR).

* Restricted to HGSOC.

* PCs are fixed to be same direct across cohorts. 

* Weighted average of K or G functions across subjects with multiple cores, weighted by the number of cells in tumor compartment.

* To be able to compute spatial trajectory, they had to have 8 cells of the cell type of interest.

* Fit models without FPCs (Model 1), with main effect (Model 2), and interaction of FPCs with abundance (1% threshold) (Model 3). Model 4 - (binary high/low FPCs at value 0).

* Reference groups: high stage (parameter is effect of low stage), low abundance (parameter is effect for high abundance).

  - stage = 0 if high and 1 if low

  - abund_binary = 0 if low and 1 if high abundance. 

* Sample Sizes (subjects)

 - AAS: 155 in Model 1, 132 in spatial models for CD3+, 109 in spatial models for CD3+CD8+.
 
 - NCO: 136 in Model 1, 118 in spatial models for CD3+, 93 for CD3+CD8+.
 
 - NECC: 175 in model 1, 156 in spatial models for CD3+, 119 for CD3+CD8+. 
 
 - NHS: 239 in model 1, 192 in model for CD3+, 128 for CD3+CD8+.
 
 - NHSII: 68 in model 1, 56 in model for CD3+, 45 in model for CD3+CD8+.
 



```{r data, ECHO=FALSE}

#reading in Abundance + Spatial Possible Model (all subjects), model 1

cyto.g.1 <- read_excel("data1_g.xlsx", sheet= "Abundance and Func Observed")

# cyto.k.1 <- read_excel("data1_k.xlsx", sheet= "Abundance and Func Observed")

tcell.g.1 <- read_excel("data1_g.xlsx", sheet= "Abundance and Func Observed")

# tcell.k.1 <- read_excel("data1_k.xlsx", sheet= "Abundance and Func Observed")



#reading in the FPC Score with No interaction in Model 2

cyto.g.2 <- read_excel("data2_g.xlsx", sheet= "FPC Score No Interactions")

# cyto.k.2 <- read_excel("data2_k.xlsx", sheet= "FPC Score No Interactions")

tcell.g.2 <- read_excel("data2_g.xlsx", sheet= "FPC Score No Interactions")

# tcell.k.2 <- read_excel("data2_k.xlsx", sheet= "FPC Score No Interactions")



#reading in the FPC Score for interaction in Model 3

cyto.g.3 <- read_excel("data3_g.xlsx", sheet= "FPC Score Interactions")

# cyto.k.3 <- read_excel("data3_k.xlsx", sheet= "FPC Score Interactions")

tcell.g.3 <-read_excel("data3_g.xlsx", sheet= "FPC Score Interactions")

# tcell.k.3 <- read_excel("data3_k.xlsx", sheet= "FPC Score Interactions")



#reading in the FPC Score for interaction in Model 4 dicotomized 

cyto.g.4 <- read_excel("data4_g.xlsx", sheet= "FPC Score Interactions")

# cyto.k.4 <- read_excel("data4_k.xlsx", sheet= "FPC Score Interactions")

tcell.g.4 <- read_excel("data4_g.xlsx", sheet= "FPC Score Interactions")

# tcell.k.4 <- read_excel("data4_k.xlsx", sheet= "FPC Score Interactions")


#reading in the FPC Score for interaction in Model 4 dicotomized for FPC1 only

cyto.g.4.fpc1only <- read_excel("data5_g.xlsx", sheet= "FPC Score Interactions")

tcell.g.4.fpc1only <- read_excel("data5_g.xlsx", sheet= "FPC Score Interactions")


#fixing stage variable name in AAS and NCO

cyto.g.1$factor<-ifelse(cyto.g.1$factor == "stage_catlow stage", "stage_catlow stage", cyto.g.1$factor)
cyto.g.2$factor<-ifelse(cyto.g.2$factor == "stage_catlow stage", "stage_catlow stage", cyto.g.2$factor)
cyto.g.3$factor<-ifelse(cyto.g.3$factor == "stage_catlow stage", "stage_catlow stage", cyto.g.3$factor)
cyto.g.4$factor<-ifelse(cyto.g.4$factor == "stage_catlow stage", "stage_catlow stage", cyto.g.4$factor)
cyto.g.4.fpc1only$factor<-ifelse(cyto.g.4.fpc1only$factor == "stage_catlow stage", "stage_catlow stage", cyto.g.4.fpc1only$factor)

# cyto.k.1$factor<-ifelse(cyto.k.1$factor == "stage_catlow stage", "stage_catlow stage", cyto.k.1$factor)
# cyto.k.2$factor<-ifelse(cyto.k.2$factor == "stage_catlow stage", "stage_catlow stage", cyto.k.2$factor)
# cyto.k.3$factor<-ifelse(cyto.k.3$factor == "stage_catlow stage", "stage_catlow stage", cyto.k.3$factor)
# cyto.k.4$factor<-ifelse(cyto.k.4$factor == "stage_catlow stage", "stage_catlow stage", cyto.k.4$factor)

tcell.g.1$factor<-ifelse(tcell.g.1$factor == "stage_catlow stage", "stage_catlow stage", tcell.g.1$factor)
tcell.g.2$factor<-ifelse(tcell.g.2$factor == "stage_catlow stage", "stage_catlow stage", tcell.g.2$factor)
tcell.g.3$factor<-ifelse(tcell.g.3$factor == "stage_catlow stage", "stage_catlow stage", tcell.g.3$factor)
tcell.g.4$factor<-ifelse(tcell.g.4$factor == "stage_catlow stage", "stage_catlow stage", tcell.g.4$factor)
tcell.g.4.fpc1only$factor<-ifelse(tcell.g.4.fpc1only$factor == "stage_catlow stage", "stage_catlow stage", tcell.g.4.fpc1only$factor)

# tcell.k.1$factor<-ifelse(tcell.k.1$factor == "stage_catlow stage", "stage_catlow stage", tcell.k.1$factor)
# tcell.k.2$factor<-ifelse(tcell.k.2$factor == "stage_catlow stage", "stage_catlow stage", tcell.k.2$factor)
# tcell.k.3$factor<-ifelse(tcell.k.3$factor == "stage_catlow stage", "stage_catlow stage", tcell.k.3$factor)
# tcell.k.4$factor<-ifelse(tcell.k.4$factor == "stage_catlow stage", "stage_catlow stage", tcell.k.4$factor)

```

# Results from Abundance + Spatial Modeling Possible (Model 1)

Model 1: Survival ~ agedx + stage(low/high) + abundance(1% binary) + spatial.possible(binary)

All subjects included in analysis (not restricted to those with spatial trajectory computed).

Results are same between K and G models as not estimating K or G in models (just if spatial analysis possible).

Observe similar results for stage (higher HR for high stage), age at dx (higher HR for older individuals) and abundance (higher HR for low abundance) with survival across cohorts.

```{r meta.abundance, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%", message=FALSE}

##### Abundance
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.1, sm="HR")

tiff("forest_cd3_G_model1_abund.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Abundance (1%): CD3+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model1_abund_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Abundance (1%): CD3+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.1, sm="HR")

tiff("forest_cd3cd8_G_model1_abund.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Abundance (1%): CD3+CD8+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model1_abund_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Abundance (1%): CD3+CD8+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


##### Stage
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="stage_catlow stage", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.1, sm="HR")

tiff("forest_cd3_G_model1_stage.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Stage: CD3+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model1_stage_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Stage: CD3+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="stage_catlow stage", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.1, sm="HR")

tiff("forest_cd3cd8_G_model1_stage.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Stage: CD3+CD8+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model1_stage_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Stage: CD3+CD8+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


##### Age DX
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="ageatdx", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.1, sm="HR")

tiff("forest_cd3_G_model1_age.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Age at DX: CD3+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model1_age_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Age at DX: CD3+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="ageatdx", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.1, sm="HR")

tiff("forest_cd3cd8_G_model1_age.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Age at DX: CD3+CD8+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model1_age_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Age at DX: CD3+CD8+ model", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


```



# Results from Non-Interation Analysis (just main effects) (Model 2)

Model 2: Survival ~ agedx + stage(low/high) + abundance(1% binary) + FPC1 + FPC2


Only subjects with spatial trajectory included.

## Model 2 results for FPC1: degree of spatial clustering

Note: The estimates for FPC1 for K are very small and close to 0. Not an error in reading in data (~10-7).

See consistent results for FPC1 association with survival for G, for both T cells (CD3+) and Cytotoxic T cells (CD3+CD8+). Higher value FPC1 indicates high spatial clustering. So see worse survival (higher HR) for subjects with tumors with high spatial clustering of CD3+ and CD3+CD8+ based on G estimated curve. The association is strongest for CD3+CD8+ cell clustering. 

Don't see any relationship with respect to K. 

For NHSII, the curves are not as clean for G as for the other cohorts. For example, PC1 high/low lines cross @ radius 28 for CD3.

In general, don't see much difference in spatial trajectories for any cell types or K/G at small radii (r < 12). Radius r is in px (pixel). 

```{r meta.fpc1, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%", message=FALSE}
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.2, sm="HR")

tiff("forest_cd3_G_model2_fpc1.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("FPC1: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model2_fpc1_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("FPC1: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.2, sm="HR")

tiff("forest_cd3cd8_G_model2_fpc1.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("FPC1: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model2_fpc1_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("FPC1: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+ K
# t.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1", method.tau = "REML", random=TRUE, method.I2="Q", data = tcell.k.2, sm="HR")
# 
# forest(t.k.meta)
# grid.text("FPC1: CD3+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ K
# cyto.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1", method.tau = "REML", random=TRUE, method.I2="Q", data = cyto.k.2, sm="HR")
# 
# forest(cyto.k.meta)
# grid.text("FPC1: CD3+CD8+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

```


## Model 2 results for FPC2

See a lot of heterogeneity in estimates of relationship between FPC2 with survival across the cohorts for G and K. For K, there is not much variation in FPC2 across tumors with the high/low curves similar to the population level. 


```{r meta.fpc2, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc2", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.2, sm="HR")

tiff("forest_cd3_G_model2_fpc2.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("FPC2: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model2_fpc2_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("FPC2: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc2", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.2, sm="HR")

tiff("forest_cd3cd8_G_model2_fpc2.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("FPC2: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model2_fpc2_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("FPC2: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+ K
# t.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc2", method.tau = "REML", random=TRUE, method.I2="Q", data = tcell.k.2, sm="HR")
# 
# forest(t.k.meta)
# grid.text("FPC2: CD3+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ K
# cyto.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc2", method.tau = "REML", random=TRUE, method.I2="Q", data = cyto.k.2, sm="HR")
# 
# forest(cyto.k.meta)
# grid.text("FPC2: CD3+CD8+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

```



# Results from Interation Analysis (abundance * spatial clustering) (Model 3)

Model 3: Survival ~ Bo+ B1(agedx) + B2(stage) + B3(abundance) + B4(FPC1) + B5(FPC2) + B6(abundance x FPC1) + 
    B7(abundance x FPC2)

Only subjects with spatial trajectory included.

With significant interactions, need to look at the effects for the 4 possibilities as can't interpret main effects: low abundance / low clustering, low abundance / high clustering, high abundance / low clustering, and high abundance / high clustering. 

Need to get the mean effect for these 4 groups to compare. Abundance: 1 = high, 0 = low; FPC1: large value for clustering. 
In model 3, FPC1 and FPC2 are continuous measures.Running with binary to help with intepretation. 


## Model 3 results for Abundance (main effect)

```{r meta.fpc1.abundance, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.3, sm="HR")

tiff("forest_cd3_G_model3_abund.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 3 - Abundance: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model3_abund_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Model 3 - Abundance: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.3, sm="HR")

tiff("forest_cd3cd8_G_model3_abund.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 3 - Abundance: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model3_abund_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Model 3 - Abundance: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+ K
# t.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE, method.I2="Q", data = tcell.k.3, sm="HR")
# 
# forest(t.k.meta)
# grid.text("Model 3 - Abundance: CD3+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ K
# cyto.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE, method.I2="Q", data = cyto.k.3, sm="HR")
# 
# forest(cyto.k.meta)
# grid.text("Model 3 - Abundance: CD3+CD8+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

```

## Model 3 results for FPC1 (main effect)

```{r meta.fpc1.main, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.3, sm="HR")

tiff("forest_cd3_G_model3_fpc1.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 3 - FPC1: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model3_fpc1_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Model 3 - FPC1: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.3, sm="HR")

tiff("forest_cd3cd8_G_model3_fpc1.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 3 - FPC1: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model3_fpc1_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Model 3 - FPC1: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+ K
# t.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE, method.I2="Q", data = tcell.k.3, sm="HR")
# 
# forest(t.k.meta)
# grid.text("Model 3 - Abundance: CD3+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ K
# cyto.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE, method.I2="Q", data = cyto.k.3, sm="HR")
# 
# forest(cyto.k.meta)
# grid.text("Model 3 - Abundance: CD3+CD8+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

```


## Model 3 results for FPC1 x Abundance (inteaction effect)

```{r meta.fpc1.interaction, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.3, sm="HR")

tiff("forest_cd3_G_model3_abundfpc1.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 3 - Abundance x FPC1: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model3_abundfpc1_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Model 3 - Abundance x FPC1: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.3, sm="HR")

tiff("forest_cd3cd8_G_model3_abundfpc1.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 3 - Abundance x FPC1: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model3_abundfpc1_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Model 3 - Abundance x FPC1: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+ K
# t.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1", method.tau = "REML", random=TRUE, method.I2="Q", data = tcell.k.3, sm="HR")
# 
# forest(t.k.meta)
# grid.text("Model 3 - Abundance x FPC1: CD3+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ K
# cyto.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1", method.tau = "REML", random=TRUE, method.I2="Q", data = cyto.k.3, sm="HR")
# 
# forest(cyto.k.meta)
# grid.text("Model 3 - Abundance x FPC1: CD3+CD8+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

```



```{r meta.fpc2.interaction, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}

# SUBTITLE "## Model 3 results for FPC2 x Abundance (inteaction effect)"
# Add this subtitle back above if you want to add back FPC2 x Abundance plots

## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc2", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.3, sm="HR")

tiff("forest_cd3_G_model3_abundfpc2.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 3 - Abundance x FPC2: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model3_abundfpc2_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Model 3 - Abundance x FPC2: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc2", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.3, sm="HR")

tiff("forest_cd3cd8_G_model3_abundfpc2.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 3 - Abundance x FPC2: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model3_abundfpc2_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Model 3 - Abundance x FPC2: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+ K
# t.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc2", method.tau = "REML", random=TRUE, method.I2="Q", data = tcell.k.3, sm="HR")
# 
# forest(t.k.meta)
# grid.text("Model 3 - Abundance x FPC2: CD3+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ K
# cyto.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc2", method.tau = "REML", random=TRUE, method.I2="Q", data = cyto.k.3, sm="HR")
# 
# forest(cyto.k.meta)
# grid.text("Model 3 - Abundance x FPC2: CD3+CD8+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

```



# Results from Interation Analysis with binary FPCs (abundance * spatial clustering) (Model 4)


Model 4: Survival ~ Bo+ B1(agedx) + B2(stage) + B3(abundance) + B4(FPC1.b) + B5(FPC2.b) + B6(abundance x FPC1.b) + 
    B7(abundance x FPC2.b)

abundance = 0 if low and 1 if high.
FPC1.b = 1 if low clustering and 0 if high clustering. 

Only subjects with spatial trajectory included.

With significant interactions, need to look at the effects for the 4 possibilities as can't interpret main effects: low abundance / low clustering, low abundance / high clustering, high abundance / low clustering, and high abundance / high clustering. 


Need to get the mean effect for these 4 groups to compare. Abundance: 1 = high, 0 = low; FPC1.b: 1 = low clustering, 0 = high clustering. Holding all other variables fixed. 

low abundance / low clustering: Abundance = 0, FPC1.b = 1: B3(0)+B4(1)+B6(0) = B4 
low abundance / high clustering: abundance = 0, FPC1.b = 0: Baseline
high abundance / low clustering: abundance = 1, FPC1.b = 1: B3+B4+B6
high abundance / high clustering: abundance = 1, FPC1.b = 0: B3


```{r meta.fpc1.binary, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.4, sm="HR")

forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Abundance: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.4, sm="HR")

forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Abundance: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1_catlow", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.4, sm="HR")

forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Spatial Binary: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1_catlow", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.4, sm="HR")

forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Spatial Binary: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1_catlow", method.tau = "REML", 
                  random=TRUE, common=FALSE, method.I2="Q", data = tcell.g.4, sm="HR")

forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Abundance x Binary FPC1: CD3+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1_catlow", method.tau = "REML", 
                     random=TRUE, common=FALSE, method.I2="Q", data = cyto.g.4, sm="HR")

forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Abundance x Binary FPC1: CD3+CD8+ G Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+ K
# t.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1_catlow", method.tau = "REML", random=TRUE, method.I2="Q", data = tcell.k.4, sm="HR")
# 
# forest(t.k.meta)
# grid.text("Model 4 - Abundance x Binary FPC1: CD3+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

## CD3+CD8+ K
# cyto.k.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1_catlow", method.tau = "REML", random=TRUE, method.I2="Q", data = cyto.k.4, sm="HR")
# 
# forest(cyto.k.meta)
# grid.text("Model 4 - Abundance x FPC1: CD3+CD8+ K Estimate", .5, .95, gp=gpar(cex=1.5, fontface="bold"))

```



```{r meta.HR.mean, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}

## computing estimate of HR for each group abund/spatial

#abund = 1 if high, 0 = low; spatial cluster = 1 if low and 0 if high, 

### TCELL
##############
## aaces
aas<-tcell.g.4[tcell.g.4$cohort=="AAS",]


#high abundance, low spatial
HR.HL.aas<- exp(aas$coef[aas$factor =="abund_binary"]+aas$coef[aas$factor=="fpc1_catlow"]
  +aas$coef[aas$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.aas<- exp(aas$coef[aas$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.aas<- exp(aas$coef[aas$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.aas<-1.0

aas.hr<-rbind(HR.HL.aas, HR.HH.aas, HR.LL.aas, HR.LH.aas)
aas.hr<-as.data.frame(aas.hr)
aas.hr$group<-rownames(aas.hr)
aas.hr$HR<-aas.hr$V1

ggplot(aas.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, AACES")

##############
## ncocs
nco<-tcell.g.4[tcell.g.4$cohort=="NCO",]

#high abundance, low spatial
HR.HL.nco<- exp(nco$coef[nco$factor =="abund_binary"]+nco$coef[nco$factor=="fpc1_catlow"]
  +nco$coef[nco$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nco<- exp(nco$coef[nco$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nco<- exp(nco$coef[nco$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nco<-1.0

nco.hr<-rbind(HR.HL.nco, HR.HH.nco, HR.LL.nco, HR.LH.nco)
nco.hr<-as.data.frame(nco.hr)
nco.hr$group<-rownames(nco.hr)
nco.hr$HR<-nco.hr$V1

ggplot(nco.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, NCOCS")

##############
## necc
nec<-tcell.g.4[tcell.g.4$cohort=="NECC",]


#high abundance, low spatial
HR.HL.nec<- exp(nec$coef[nec$factor =="abund_binary"]+nec$coef[nec$factor=="fpc1_catlow"]
  +nec$coef[nec$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nec<- exp(nec$coef[nec$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nec<- exp(nec$coef[nec$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nec<-1.0

nec.hr<-rbind(HR.HL.nec, HR.HH.nec, HR.LL.nec, HR.LH.nec)
nec.hr<-as.data.frame(nec.hr)
nec.hr$group<-rownames(nec.hr)
nec.hr$HR<-nec.hr$V1

ggplot(nec.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, NECC")

##############
## nhs
nhs<-tcell.g.4[tcell.g.4$cohort=="NHS",]

#high abundance, low spatial
HR.HL.nhs<- exp(nhs$coef[nhs$factor =="abund_binary"]+nhs$coef[nhs$factor=="fpc1_catlow"]
  +nhs$coef[nhs$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nhs<- exp(nhs$coef[nhs$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nhs<- exp(nhs$coef[nhs$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nhs<-1.0

nhs.hr<-rbind(HR.HL.nhs, HR.HH.nhs, HR.LL.nhs, HR.LH.nhs)
nhs.hr<-as.data.frame(nhs.hr)
nhs.hr$group<-rownames(nhs.hr)
nhs.hr$HR<-nhs.hr$V1

ggplot(nhs.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, NHS")

##############
## nhsII
nhs2<-tcell.g.4[tcell.g.4$cohort=="NHSII",]

#high abundance, low spatial
HR.HL.nhs2<- exp(nhs2$coef[nhs2$factor =="abund_binary"]+nhs2$coef[nhs2$factor=="fpc1_catlow"]
  +nhs2$coef[nhs2$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nhs2<- exp(nhs2$coef[nhs2$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nhs2<- exp(nhs2$coef[nhs2$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nhs2<-1.0

nhs2.hr<-rbind(HR.HL.nhs2, HR.HH.nhs2, HR.LL.nhs2, HR.LH.nhs2)
nhs2.hr<-as.data.frame(nhs2.hr)
nhs2.hr$group<-rownames(nhs2.hr)
nhs2.hr$HR<-nhs2.hr$V1

ggplot(nhs2.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, NHSII")

### CYTOTOXIC TCELL
##############
## aaces
aas<-cyto.g.4[cyto.g.4$cohort=="AAS",]


#high abundance, low spatial
HR.HL.aas<- exp(aas$coef[aas$factor =="abund_binary"]+aas$coef[aas$factor=="fpc1_catlow"]
  +aas$coef[aas$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.aas<- exp(aas$coef[aas$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.aas<- exp(aas$coef[aas$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.aas<-1.0

aas.hr<-rbind(HR.HL.aas, HR.HH.aas, HR.LL.aas, HR.LH.aas)
aas.hr<-as.data.frame(aas.hr)
aas.hr$group<-rownames(aas.hr)
aas.hr$HR<-aas.hr$V1

ggplot(aas.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, AACES")

##############
## ncocs
nco<-cyto.g.4[cyto.g.4$cohort=="NCO",]

#high abundance, low spatial
HR.HL.nco<- exp(nco$coef[nco$factor =="abund_binary"]+nco$coef[nco$factor=="fpc1_catlow"]
  +nco$coef[nco$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nco<- exp(nco$coef[nco$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nco<- exp(nco$coef[nco$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nco<-1.0

nco.hr<-rbind(HR.HL.nco, HR.HH.nco, HR.LL.nco, HR.LH.nco)
nco.hr<-as.data.frame(nco.hr)
nco.hr$group<-rownames(nco.hr)
nco.hr$HR<-nco.hr$V1

ggplot(nco.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, NCOCS")

##############
## necc
nec<-cyto.g.4[cyto.g.4$cohort=="NECC",]


#high abundance, low spatial
HR.HL.nec<- exp(nec$coef[nec$factor =="abund_binary"]+nec$coef[nec$factor=="fpc1_catlow"]
  +nec$coef[nec$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nec<- exp(nec$coef[nec$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nec<- exp(nec$coef[nec$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nec<-1.0

nec.hr<-rbind(HR.HL.nec, HR.HH.nec, HR.LL.nec, HR.LH.nec)
nec.hr<-as.data.frame(nec.hr)
nec.hr$group<-rownames(nec.hr)
nec.hr$HR<-nec.hr$V1

ggplot(nec.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, NECC")

##############
## nhs
nhs<-cyto.g.4[cyto.g.4$cohort=="NHS",]

#high abundance, low spatial
HR.HL.nhs<- exp(nhs$coef[nhs$factor =="abund_binary"]+nhs$coef[nhs$factor=="fpc1_catlow"]
  +nhs$coef[nhs$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nhs<- exp(nhs$coef[nhs$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nhs<- exp(nhs$coef[nhs$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nhs<-1.0

nhs.hr<-rbind(HR.HL.nhs, HR.HH.nhs, HR.LL.nhs, HR.LH.nhs)
nhs.hr<-as.data.frame(nhs.hr)
nhs.hr$group<-rownames(nhs.hr)
nhs.hr$HR<-nhs.hr$V1

ggplot(nhs.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, NHS")

##############
## nhsII
nhs2<-cyto.g.4[cyto.g.4$cohort=="NHSII",]

#high abundance, low spatial
HR.HL.nhs2<- exp(nhs2$coef[nhs2$factor =="abund_binary"]+nhs2$coef[nhs2$factor=="fpc1_catlow"]
  +nhs2$coef[nhs2$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nhs2<- exp(nhs2$coef[nhs2$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nhs2<- exp(nhs2$coef[nhs2$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nhs2<-1.0

nhs2.hr<-rbind(HR.HL.nhs2, HR.HH.nhs2, HR.LL.nhs2, HR.LH.nhs2)
nhs2.hr<-as.data.frame(nhs2.hr)
nhs2.hr$group<-rownames(nhs2.hr)
nhs2.hr$HR<-nhs2.hr$V1

ggplot(nhs2.hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, NHSII")


### HR from META random effects

## T cells
abundance.meta<-log(1.0)
spatial.meta<-log(1.21)
interaction.meta<-log(0.61)

hr.hh<-exp(abundance.meta)
hr.hl<-exp(abundance.meta+spatial.meta+interaction.meta)
hr.ll<-exp(spatial.meta)
hr.lh<-1

hr<-rbind(hr.hh, hr.hl, hr.ll, hr.lh)

hr<-as.data.frame(hr)
hr$group<-rownames(hr)
hr$HR<-hr$V1

ggplot(hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Meta Analysis for T cells, G")
  
hr
 
## Cyto cells
abundance.meta<-log(0.78)
spatial.meta<-log(0.87)
interaction.meta<-log(0.60)

hr.hh<-exp(abundance.meta)
hr.hl<-exp(abundance.meta+spatial.meta+interaction.meta)
hr.ll<-exp(spatial.meta)
hr.lh<-1

hr<-rbind(hr.hh, hr.hl, hr.ll, hr.lh)

hr<-as.data.frame(hr)
hr$group<-rownames(hr)
hr$HR<-hr$V1

ggplot(hr, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Meta Analysis for Cytotoxic T cells, G")
  
hr
```




## Model 4 from Interation Analysis with binary FPCs (abundance * spatial clustering) FPC1 ONLY

```{r meta.fpc1.binary.fpc1only, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}
## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.4.fpc1only, sm="HR")

tiff("forest_cd3_G_model4_abund.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Abundance: CD3+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model4_abund_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Model 4 - Abundance: CD3+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.4.fpc1only, sm="HR")

tiff("forest_cd3cd8_G_model4_abund.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Abundance: CD3+CD8+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model4_abund_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Model 4 - Abundance: CD3+CD8+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1_catlow", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = tcell.g.4.fpc1only, sm="HR")

tiff("forest_cd3_G_model4_fpc1bin.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Spatial Binary: CD3+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model4_fpc1bin_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Model 4 - Spatial Binary: CD3+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="fpc1_catlow", method.tau = "REML", random=TRUE,
                  common=FALSE, method.I2="Q", data = cyto.g.4.fpc1only, sm="HR")

tiff("forest_cd3cd8_G_model4_fpc1bin.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Spatial Binary: CD3+CD8+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model4_fpc1bin_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Model 4 - Spatial Binary: CD3+CD8+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()



## CD3+ G
t.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1_catlow", method.tau = "REML", 
                  random=TRUE, common=FALSE, method.I2="Q", data = tcell.g.4.fpc1only, sm="HR")

tiff("forest_cd3_G_model4_abundfpc1bin.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Abundance x Binary FPC1: CD3+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3_G_model4_abundfpc1bin_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(t.g.meta)
grid.text("Model 4 - Abundance x Binary FPC1: CD3+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()


## CD3+CD8+ G
cyto.g.meta<-metagen(coef, `se(coef)`, studlab=cohort, subset=factor=="abund_binary:fpc1_catlow", method.tau = "REML", 
                     random=TRUE, common=FALSE, method.I2="Q", data = cyto.g.4.fpc1only, sm="HR")

tiff("forest_cd3cd8_G_model4_abundfpc1bin.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta, leftcols="studlab", leftlabs="Study", rightcols=c("effect","ci","w.random"),
       rightlabs=c("HR","95%-CI","Weight (random)"), comb.fixed=FALSE, comb.random=TRUE, print.pval.Q=FALSE,
       print.I2=FALSE, print.tau2=FALSE)
grid.text("Model 4 - Abundance x Binary FPC1: CD3+CD8+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()

tiff("forest_cd3cd8_G_model4_abundfpc1bin_full.tiff", width = 10, height = 5, units = "in",
     res = 300, compression = "lzw")
forest(cyto.g.meta)
grid.text("Model 4 - Abundance x Binary FPC1: CD3+CD8+ G Estimate (FPC1 ONLY)", .5, .95, gp=gpar(cex=1.5, fontface="bold"))
dev.off()



```



```{r meta.HR.mean.fpc1only, ECHO=FALSE, fig.width=10, fig.height=5, out.width="100%"}

## computing estimate of HR for each group abund/spatial

#abund = 1 if high, 0 = low; spatial cluster = 1 if low and 0 if high, 

### TCELL
##############
## aaces
aas.fpc1only<-tcell.g.4.fpc1only[tcell.g.4.fpc1only$cohort=="AAS",]


#high abundance, low spatial
HR.HL.aas.fpc1only<- exp(aas.fpc1only$coef[aas.fpc1only$factor =="abund_binary"]+aas.fpc1only$coef[aas.fpc1only$factor=="fpc1_catlow"]
  +aas.fpc1only$coef[aas.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.aas.fpc1only<- exp(aas.fpc1only$coef[aas.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.aas.fpc1only<- exp(aas.fpc1only$coef[aas.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.aas.fpc1only<-1.0

aas.hr.fpc1only<-rbind(HR.HL.aas.fpc1only, HR.HH.aas.fpc1only, HR.LL.aas.fpc1only, HR.LH.aas.fpc1only)
aas.hr.fpc1only<-as.data.frame(aas.hr.fpc1only)
aas.hr.fpc1only$group<-rownames(aas.hr.fpc1only)
aas.hr.fpc1only$HR<-aas.hr.fpc1only$V1

ggplot(aas.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, AACES (FPC1 ONLY)")

##############
## ncocs
nco.fpc1only<-tcell.g.4.fpc1only[tcell.g.4.fpc1only$cohort=="NCO",]

#high abundance, low spatial
HR.HL.nco.fpc1only<- exp(nco.fpc1only$coef[nco.fpc1only$factor =="abund_binary"]+nco.fpc1only$coef[nco.fpc1only$factor=="fpc1_catlow"]
  +nco.fpc1only$coef[nco.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nco.fpc1only<- exp(nco.fpc1only$coef[nco.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nco.fpc1only<- exp(nco.fpc1only$coef[nco.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nco.fpc1only<-1.0

nco.hr.fpc1only<-rbind(HR.HL.nco.fpc1only, HR.HH.nco.fpc1only, HR.LL.nco.fpc1only, HR.LH.nco.fpc1only)
nco.hr.fpc1only<-as.data.frame(nco.hr.fpc1only)
nco.hr.fpc1only$group<-rownames(nco.hr.fpc1only)
nco.hr.fpc1only$HR<-nco.hr.fpc1only$V1

ggplot(nco.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, NCOCS (FPC1 ONLY)")

##############
## necc
nec.fpc1only<-tcell.g.4.fpc1only[tcell.g.4.fpc1only$cohort=="NECC",]


#high abundance, low spatial
HR.HL.nec.fpc1only<- exp(nec.fpc1only$coef[nec.fpc1only$factor =="abund_binary"]+nec.fpc1only$coef[nec.fpc1only$factor=="fpc1_catlow"]
  +nec.fpc1only$coef[nec.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nec.fpc1only<- exp(nec.fpc1only$coef[nec.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nec.fpc1only<- exp(nec.fpc1only$coef[nec.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nec.fpc1only<-1.0

nec.hr.fpc1only<-rbind(HR.HL.nec.fpc1only, HR.HH.nec.fpc1only, HR.LL.nec.fpc1only, HR.LH.nec.fpc1only)
nec.hr.fpc1only<-as.data.frame(nec.hr.fpc1only)
nec.hr.fpc1only$group<-rownames(nec.hr.fpc1only)
nec.hr.fpc1only$HR<-nec.hr.fpc1only$V1

ggplot(nec.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, NECC (FPC1 ONLY)")

##############
## nhs
nhs.fpc1only<-tcell.g.4.fpc1only[tcell.g.4.fpc1only$cohort=="NHS",]

#high abundance, low spatial
HR.HL.nhs.fpc1only<- exp(nhs.fpc1only$coef[nhs.fpc1only$factor =="abund_binary"]+nhs.fpc1only$coef[nhs.fpc1only$factor=="fpc1_catlow"]
  +nhs.fpc1only$coef[nhs.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nhs.fpc1only<- exp(nhs.fpc1only$coef[nhs.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nhs.fpc1only<- exp(nhs.fpc1only$coef[nhs.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nhs.fpc1only<-1.0

nhs.hr.fpc1only<-rbind(HR.HL.nhs.fpc1only, HR.HH.nhs.fpc1only, HR.LL.nhs.fpc1only, HR.LH.nhs.fpc1only)
nhs.hr.fpc1only<-as.data.frame(nhs.hr.fpc1only)
nhs.hr.fpc1only$group<-rownames(nhs.hr.fpc1only)
nhs.hr.fpc1only$HR<-nhs.hr.fpc1only$V1

ggplot(nhs.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, NHS (FPC1 ONLY)")

##############
## nhsII
nhs2.fpc1only<-tcell.g.4.fpc1only[tcell.g.4.fpc1only$cohort=="NHSII",]

#high abundance, low spatial
HR.HL.nhs2.fpc1only<- exp(nhs2.fpc1only$coef[nhs2.fpc1only$factor =="abund_binary"]+nhs2.fpc1only$coef[nhs2.fpc1only$factor=="fpc1_catlow"]
  +nhs2.fpc1only$coef[nhs2.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nhs2.fpc1only<- exp(nhs2.fpc1only$coef[nhs2.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nhs2.fpc1only<- exp(nhs2.fpc1only$coef[nhs2.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nhs2.fpc1only<-1.0

nhs2.hr.fpc1only<-rbind(HR.HL.nhs2.fpc1only, HR.HH.nhs2.fpc1only, HR.LL.nhs2.fpc1only, HR.LH.nhs2.fpc1only)
nhs2.hr.fpc1only<-as.data.frame(nhs2.hr.fpc1only)
nhs2.hr.fpc1only$group<-rownames(nhs2.hr.fpc1only)
nhs2.hr.fpc1only$HR<-nhs2.hr.fpc1only$V1

ggplot(nhs2.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Tcell, NHSII (FPC1 ONLY)")

### CYTOTOXIC TCELL
##############
## aaces
aas.fpc1only<-cyto.g.4.fpc1only[cyto.g.4.fpc1only$cohort=="AAS",]


#high abundance, low spatial
HR.HL.aas.fpc1only<- exp(aas.fpc1only$coef[aas.fpc1only$factor =="abund_binary"]+aas.fpc1only$coef[aas.fpc1only$factor=="fpc1_catlow"]
  +aas.fpc1only$coef[aas.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.aas.fpc1only<- exp(aas.fpc1only$coef[aas.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.aas.fpc1only<- exp(aas.fpc1only$coef[aas.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.aas.fpc1only<-1.0

aas.hr.fpc1only<-rbind(HR.HL.aas.fpc1only, HR.HH.aas.fpc1only, HR.LL.aas.fpc1only, HR.LH.aas.fpc1only)
aas.hr.fpc1only<-as.data.frame(aas.hr.fpc1only)
aas.hr.fpc1only$group<-rownames(aas.hr.fpc1only)
aas.hr.fpc1only$HR<-aas.hr.fpc1only$V1

ggplot(aas.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, AACES (FPC1 ONLY)")

##############
## ncocs
nco.fpc1only<-cyto.g.4.fpc1only[cyto.g.4.fpc1only$cohort=="NCO",]

#high abundance, low spatial
HR.HL.nco.fpc1only<- exp(nco.fpc1only$coef[nco.fpc1only$factor =="abund_binary"]+nco.fpc1only$coef[nco.fpc1only$factor=="fpc1_catlow"]
  +nco.fpc1only$coef[nco.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nco.fpc1only<- exp(nco.fpc1only$coef[nco.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nco.fpc1only<- exp(nco.fpc1only$coef[nco.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nco.fpc1only<-1.0

nco.hr.fpc1only<-rbind(HR.HL.nco.fpc1only, HR.HH.nco.fpc1only, HR.LL.nco.fpc1only, HR.LH.nco.fpc1only)
nco.hr.fpc1only<-as.data.frame(nco.hr.fpc1only)
nco.hr.fpc1only$group<-rownames(nco.hr.fpc1only)
nco.hr.fpc1only$HR<-nco.hr.fpc1only$V1

ggplot(nco.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, NCOCS (FPC1 ONLY)")

##############
## necc
nec.fpc1only<-cyto.g.4.fpc1only[cyto.g.4.fpc1only$cohort=="NECC",]


#high abundance, low spatial
HR.HL.nec.fpc1only<- exp(nec.fpc1only$coef[nec.fpc1only$factor =="abund_binary"]+nec.fpc1only$coef[nec.fpc1only$factor=="fpc1_catlow"]
  +nec.fpc1only$coef[nec.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nec.fpc1only<- exp(nec.fpc1only$coef[nec.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nec.fpc1only<- exp(nec.fpc1only$coef[nec.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nec.fpc1only<-1.0

nec.hr.fpc1only<-rbind(HR.HL.nec.fpc1only, HR.HH.nec.fpc1only, HR.LL.nec.fpc1only, HR.LH.nec.fpc1only)
nec.hr.fpc1only<-as.data.frame(nec.hr.fpc1only)
nec.hr.fpc1only$group<-rownames(nec.hr.fpc1only)
nec.hr.fpc1only$HR<-nec.hr.fpc1only$V1

ggplot(nec.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, NECC (FPC1 ONLY)")

##############
## nhs
nhs.fpc1only<-cyto.g.4.fpc1only[cyto.g.4.fpc1only$cohort=="NHS",]

#high abundance, low spatial
HR.HL.nhs.fpc1only<- exp(nhs.fpc1only$coef[nhs.fpc1only$factor =="abund_binary"]+nhs.fpc1only$coef[nhs.fpc1only$factor=="fpc1_catlow"]
  +nhs.fpc1only$coef[nhs.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nhs.fpc1only<- exp(nhs.fpc1only$coef[nhs.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nhs.fpc1only<- exp(nhs.fpc1only$coef[nhs.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nhs.fpc1only<-1.0

nhs.hr.fpc1only<-rbind(HR.HL.nhs.fpc1only, HR.HH.nhs.fpc1only, HR.LL.nhs.fpc1only, HR.LH.nhs.fpc1only)
nhs.hr.fpc1only<-as.data.frame(nhs.hr.fpc1only)
nhs.hr.fpc1only$group<-rownames(nhs.hr.fpc1only)
nhs.hr.fpc1only$HR<-nhs.hr.fpc1only$V1

ggplot(nhs.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, NHS (FPC1 ONLY)")

##############
## nhsII
nhs2.fpc1only<-cyto.g.4.fpc1only[cyto.g.4.fpc1only$cohort=="NHSII",]

#high abundance, low spatial
HR.HL.nhs2.fpc1only<- exp(nhs2.fpc1only$coef[nhs2.fpc1only$factor =="abund_binary"]+nhs2.fpc1only$coef[nhs2.fpc1only$factor=="fpc1_catlow"]
  +nhs2.fpc1only$coef[nhs2.fpc1only$factor== "abund_binary:fpc1_catlow"])

#high abundance, high spatial 
HR.HH.nhs2.fpc1only<- exp(nhs2.fpc1only$coef[nhs2.fpc1only$factor =="abund_binary"])


#low abundance, low spatial
HR.LL.nhs2.fpc1only<- exp(nhs2.fpc1only$coef[nhs2.fpc1only$factor=="fpc1_catlow"])

## low abundance, high spatial
HR.LH.nhs2.fpc1only<-1.0

nhs2.hr.fpc1only<-rbind(HR.HL.nhs2.fpc1only, HR.HH.nhs2.fpc1only, HR.LL.nhs2.fpc1only, HR.LH.nhs2.fpc1only)
nhs2.hr.fpc1only<-as.data.frame(nhs2.hr.fpc1only)
nhs2.hr.fpc1only$group<-rownames(nhs2.hr.fpc1only)
nhs2.hr.fpc1only$HR<-nhs2.hr.fpc1only$V1

ggplot(nhs2.hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Cytotoxic T cells, NHSII (FPC1 ONLY)")


### HR from META random effects

## T cells
abundance.meta.fpc1only<-log(1.08)
spatial.meta.fpc1only<-log(1.23)
interaction.meta.fpc1only<-log(0.62)

hr.hh.fpc1only<-exp(abundance.meta.fpc1only)
hr.hl.fpc1only<-exp(abundance.meta.fpc1only+spatial.meta.fpc1only+interaction.meta.fpc1only)
hr.ll.fpc1only<-exp(spatial.meta.fpc1only)
hr.lh.fpc1only<-1

hr.fpc1only<-rbind(hr.hh.fpc1only, hr.hl.fpc1only, hr.ll.fpc1only, hr.lh.fpc1only)

hr.fpc1only<-as.data.frame(hr.fpc1only)
hr.fpc1only$group<-rownames(hr.fpc1only)
hr.fpc1only$HR<-hr.fpc1only$V1

ggplot(hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Meta Analysis for T cells, G (FPC1 ONLY)")
  
hr.fpc1only
 
## Cyto cells
abundance.meta.fpc1only<-log(0.81)
spatial.meta.fpc1only<-log(0.84)
interaction.meta.fpc1only<-log(0.63)

hr.hh.fpc1only<-exp(abundance.meta.fpc1only)
hr.hl.fpc1only<-exp(abundance.meta.fpc1only+spatial.meta.fpc1only+interaction.meta.fpc1only)
hr.ll.fpc1only<-exp(spatial.meta.fpc1only)
hr.lh.fpc1only<-1

hr.fpc1only<-rbind(hr.hh.fpc1only, hr.hl.fpc1only, hr.ll.fpc1only, hr.lh.fpc1only)

hr.fpc1only<-as.data.frame(hr.fpc1only)
hr.fpc1only$group<-rownames(hr.fpc1only)
hr.fpc1only$HR<-hr.fpc1only$V1

ggplot(hr.fpc1only, aes(group, HR))+
  geom_bar(stat="identity", fill = "steelblue")+
  ggtitle("Meta Analysis for Cytotoxic T cells, G (FPC1 ONLY)")
  
hr.fpc1only
```





